Tracing R Base: +

### 2019-05-05 notebooks/rplus.Rmd
fixed optionals for brackets, and pushing data for that too

```{r}
# technically in L2
base_df <- readRDS("../data/some_plus_examples.RDS")

@@

@@

>>>>

```{r}
# technically in L2
# base_df <- readRDS("../data/some_plus_examples.RDS")
# base_df <- readRDS("../data/base_with_plus_and_brack.RDS")
base_df <- readRDS("../data/base_with_brack_fixed.RDS")

@@

# just get [

subtype_df_L0_b <- filter(subtype_df_L0, fun == "[") %>% salient_only_one_fun(just_types = F)
subtype_df_L1_b <- filter(subtype_df_L1, fun == "[") %>% salient_only_one_fun(just_types = F)
subtype_df_L2_b <- filter(subtype_df_L2, fun == "[") %>% salient_only_one_fun(just_types=F)

@@

] is somewhat interesting.
There were some issues with ].
The number of arguments that it takes is somewhat related to the dimensions of the thing being indexed.
For example, in data frames you can have a call to ] with 3 arguments: the data frame first, followed by the row and then column numbers (optionally).
For lists, it's always just 2 arguments.
Not sure how ... best to deal with this.
Right now, I just have it take 2 arguments: the thing being accessed, and an index variable.

There is perhaps room for a more sophisticateed analysis here, looking at the domensions of the first argument.
I don't think it'll be too challenging, but again, do we want to go that far?
I think that would be useful for some IDE tool or something: for instance, telling the programmer that they aren't using the thing with the right amount of dimensions.
Then again, you can totally do that and it's completely fine...

TODO: What package has the call with 1 argument?
